Real Estate

### 2022-10-21 src/real_estate.Rmd
reading google sheet urls

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(googlesheets4)

MSA_demo_data <- read_sheet("https://docs.google.com/spreadsheets/d/12do9sRCAcrIe0K-VcJWXNmmTm_jg5rKjZ0NeJPOm9Jw/edit#gid=0")
city_realEstate_ata <- read_sheet("https://docs.google.com/spreadsheets/d/12do9sRCAcrIe0K-VcJWXNmmTm_jg5rKjZ0NeJPOm9Jw/edit#gid=359643482")
```
